A Greedy-based calculation method of RBS maximum allowable current

### 2023-05-23 paper/simple_for_2docx.tex
优化latex2word的效果

In addition to the equivalent circuit assumptions, we also assume that all batteries have the same internal resistance value $r_b$ and supply the same electric potential $u_s$ to simplify the model.
Then the output current $I_o$ and each battery's current $\bm{I}_b$ can be given by solving the simultaneous Eq. \ref{eq:Kirchhoffs_law} and \ref{eq:generalized_branches} eventually.
Let
\begin{equation}\label{eq:Yn}
    \bm{Y}_n (\bm{X}_s) = \frac{1}{R_o} \bm{A}_o\bm{A}_o^\T + \frac{1}{r_b} \bm{A}_b\bm{A}_b^\T + \frac{1}{r_s}\bm{A}_s\bm{X}_s\bm{A}_s^\T,
\end{equation}
where $R_o$ is the equivalent resistance of the external circuit.
Then, if $\bm{Y}_n$ is an invertible matrix,
\begin{align}
    I_o(\bm{X}_s)      & = \frac{u_b}{R_o r_b} \bm{A}_o^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b \bm{I}_{N_b\times 1};\label{eq:I_o}\\
    \bm{I}_b(\bm{X}_s) & = \frac{u_b}{r_b^2}[\bm{A}_b^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b\bm{I}_{N_b \times 1}  -r_b \bm{I}_{N_b \times 1}],\label{eq:I_b}
\end{align}
where $\bm{I}_{N_b\times 1}$ is a column vector with all equal to 1.

In this study, the ratio of $I_o$ and $\max (\bm{I}_b)$ is used to characterize the maximum allowable current for a given RBS architecture, denoted as $\eta$:
\begin{equation}\label{eq:eta}
    \eta = \frac{I_o}{\max (\bm{I}_b)}.
\end{equation}
The discussion in the next section will show that the $\eta$ reflects the ability of the RBS architecture itself to deliver current, regardliess of the battery cells used by the RBS.
Finally the problem in RBS can be formulated as
\begin{align}
    & \max \eta \label{eq:max_eta}\\
    \text{s.t.} & \max (\bm{I}_b) \leq I_m, \label{eq:Ib_leq_Im}
\end{align}
where $I_m$ is the maximum allowable current of the battery; $\eta$ can be calculated by Eq. \ref{eq:eta}; $I_o$ and $\bm{I}_b$ can be calculated by Eq. \ref{eq:I_o} and \ref{eq:I_b}.
However, it is computationally difficult to solve \ref{eq:max_eta} directly because of the presence of matrix $\bm{Y}_n^{-1}$.
As the number of batteries and switches in the RBS increase, the order of the matrix increases, and the time costed to compute increases sharply.
A greedy algorithm will be proposed to solve this problem in the next subsection.

@@

\tikzset{
  meta box/.style={
    draw,
    black,
    very thick,
    text centered,
  },
  punkt/.style={
    meta box,
    rectangle,
    rounded corners,
    inner sep=.25em,
    minimum height=2em,
    minimum width=4em,
    align=center,
    text width=10em
  },
  round/.style={
    meta box,
    circle,
    minimum size=0,
    inner sep=0pt, 
    outer sep=0pt
  },
  every fit/.style={
    draw,
    thick,
    dashed,
    gray,
    inner xsep=.5em,
    inner ysep=.75em
  }
}
\begin{figure}
\begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
    \node[punkt]     (input) {Input: RBS structure};
    \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Eqs. \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
    \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Eq. \ref{eq:A}};
    \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
    \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{set}$ batteries from $N_b$};
    \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
    \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{set}$ converged?};
    \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{set}$ by dichotomy};
    \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
        select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
        if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
        $\bm{X}[j]=1$ else $0$};
    \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Eq.\ref{eq:Yn}};
    \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
    \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
    \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Eqs. \ref{eq:I_o} and \ref{eq:I_b}};
    \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
    \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
    \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Eq.\ref{eq:eta}};
    \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
    \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
    \node[round,left=1.5of update_max_eta](point1){};

    \graph{
      (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
      (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
      (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
      (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
      (is_Nset_converged) ->["Yes"] (output);
      (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
    };
\end{tikzpicture}
\caption{The computational flowchart of the proposed method in this paper.}\label{fig:flowchart}
\end{figure}
\section{Case Study}

@@

The correctness of the results shown in Fig. \ref{fig:ef-mac} is obvious. 
When B1 and B2 or B3 and B4 are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e. twice the current output of a single battery in RBS.
While adding more batteries to the main circuit can only form a series structure and will not improve the MAC.
It is worth noting that when solving for MAC, $\eta$ is used as the objective function instead of $I_o$, which makes the result of MAC more reasonable. 
According to the results shown in Tab. \ref{tab:find_mac}, $I_o$ and $\bm{I}_b$ are affected by the equivalent resistance $R_o$ of external electrical appliance, the battery's electromotive force $u_b$, and internal resistance $r_b$. 
This means that if $I_o$ is used as the objective function, even for the same RBS structure, the MAC result and corresponding switch state could be changed due to different external electrical appliances. 
This increases the difficulty and uncertainty in RBS structure design. 
On the contrary, by using $\eta$ as the objective function, which dividing $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results is eliminated, as shown in Tabs. \ref{tab:given_x} and \ref{tab:find_mac}.
$\eta$ only reflects the maximum output current capability of the RBS structure.
Assuming that the maximum allowed current of battery cells in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by calculating the $\eta$ of the structure. 
Therefore, compared to $I_o$, $\eta$ is more suitable for structure design. 
Most of the currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} have simple topological characteristics, and the calculation of MACs are relatively simple, even intuitive. % #TODO 添加cite
However, when complex and flexible structures need to be designed for application scenarios such as equalization or isolation of specific battery cells, the estimation of MAC will become complex and complicated. 
The method proposed in this paper can effectively solve any RBS structure and estimate MAC universally, paving the way for the structure design of more complex and flexible RBSs.

@@

\section{Appendix} %TODO 待修改
\begin{algorithm}
    \caption{Get the max available currents of a certain RBS}\label{alg:eta_RBS}
    \KwData{Directed graph model $G(V,E)$ of the RBS}
    \KwResult{$\max \eta$}
    \For{$i \in E_b$}{
        $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
        $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
    }
    get $\bm{A}$ by Equation \ref{eq:A}\;
    \While{not yet determine $\max \eta$ }
    {
        $N_{sel} \leftarrow \text{number of selected $SP$s calculated by dichotomy}$\;
        $C_b    \leftarrow \text{set of all combinations of $N_{sel} $~batteries from $N_b$}$\;
        \For{$c_b \in C_b$}{
            $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
            $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
            get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
            \eIf{$\bm{Y}_n$ is invertible}{
            }{construct an effective solution}
            get $I_o$ by Equation \ref{eq:I_o}\;
            get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
            \eIf{$\max(\bm{I}_b)\leq I_m$}{
                $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
            }{break}
        }
    }
\end{algorithm}

\bibliographystyle{ieeetr}
% \bibliography{../attachments/my_ref}
\bibliography{my_ref}

>>>>

In addition to the equivalent circuit assumptions, we also assume that all batteries have the same internal resistance value $r_b$ and supply the same electric potential $u_s$ to simplify the model.
Then the output current $I_o$ and each battery's current $\bm{I}_b$ can be given by solving the simultaneous Eq. \ref{eq:Kirchhoffs_law} and \ref{eq:generalized_branches} eventually.
Let
\begin{equation}\label{eq:Yn}
    \bm{Y}_n (\bm{X}_s) = \frac{1}{R_o} \bm{A}_o\bm{A}_o^\T + \frac{1}{r_b} \bm{A}_b\bm{A}_b^\T + \frac{1}{r_s}\bm{A}_s\bm{X}_s\bm{A}_s^\T,
\end{equation}
where $R_o$ is the equivalent resistance of the external circuit.
Then, if $\bm{Y}_n$ is an invertible matrix,
\begin{equation}
    I_o(\bm{X}_s)       = \frac{u_b}{R_o r_b} \bm{A}_o^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b \bm{I}_{N_b\times 1};\label{eq:I_o}
\end{equation}
\begin{equation}
    \bm{I}_b(\bm{X}_s)  = \frac{u_b}{r_b^2}[\bm{A}_b^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b\bm{I}_{N_b \times 1}  -r_b \bm{I}_{N_b \times 1}],\label{eq:I_b}
\end{equation}
where $\bm{I}_{N_b\times 1}$ is a column vector with all equal to 1.

In this study, the ratio of $I_o$ and $\max (\bm{I}_b)$ is used to characterize the maximum allowable current for a given RBS architecture, denoted as $\eta$:
\begin{equation}\label{eq:eta}
    \eta = \frac{I_o}{\max (\bm{I}_b)}.
\end{equation}
The discussion in the next section will show that the $\eta$ reflects the ability of the RBS architecture itself to deliver current, regardliess of the battery cells used by the RBS.
Finally the problem in RBS can be formulated as
\begin{align}
    & \max \eta \label{eq:max_eta}\\
    \text{s.t.} & \max (\bm{I}_b) \leq I_m, \label{eq:Ib_leq_Im}
\end{align}
where $I_m$ is the maximum allowable current of the battery; $\eta$ can be calculated by Eq. \ref{eq:eta}; $I_o$ and $\bm{I}_b$ can be calculated by Eq. \ref{eq:I_o} and \ref{eq:I_b}.
However, it is computationally difficult to solve Eq. \ref{eq:max_eta} directly because of the presence of matrix $\bm{Y}_n^{-1}$.
As the number of batteries and switches in the RBS increase, the order of the matrix increases, and the time costed to compute increases sharply.
A greedy algorithm will be proposed to solve this problem in the next subsection.

@@

\tikzset{
  meta box/.style={
    draw,
    black,
    very thick,
    text centered,
  },
  punkt/.style={
    meta box,
    rectangle,
    rounded corners,
    inner sep=.25em,
    minimum height=2em,
    minimum width=4em,
    align=center,
    text width=10em
  },
  round/.style={
    meta box,
    circle,
    minimum size=0,
    inner sep=0pt, 
    outer sep=0pt
  },
  every fit/.style={
    draw,
    thick,
    dashed,
    gray,
    inner xsep=.5em,
    inner ysep=.75em
  }
}
\begin{figure}
% \begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
%     \node[punkt]     (input) {Input: RBS structure};
%     \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Eqs. \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
%     \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Eq. \ref{eq:A}};
%     \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
%     \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{set}$ batteries from $N_b$};
%     \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
%     \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{set}$ converged?};
%     \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{set}$ by dichotomy};
%     \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
%         select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
%         if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
%         $\bm{X}[j]=1$ else $0$};
%     \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Eq.\ref{eq:Yn}};
%     \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
%     \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
%     \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Eqs. \ref{eq:I_o} and \ref{eq:I_b}};
%     \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
%     \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
%     \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Eq.\ref{eq:eta}};
%     \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
%     \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
%     \node[round,left=1.5of update_max_eta](point1){};
% 
%     \graph{
%       (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
%       (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
%       (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
%       (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
%       (is_Nset_converged) ->["Yes"] (output);
%       (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
%     };
% \end{tikzpicture}
    \centering
    \includegraphics[width=\textwidth]{../attachments/IMG_20230411_225909.jpg}
\caption{The computational flowchart of the proposed method in this paper.}\label{fig:flowchart}
\end{figure}
\section{Case Study}

@@

The correctness of the results shown in Fig. \ref{fig:ef-mac} is obvious. 
When B1 and B2 or B3 and B4 are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e. twice the current output of a single battery in RBS.
While adding more batteries to the main circuit can only form a series structure and will not improve the MAC.
It is worth noting that when solving for MAC, $\eta$ is used as the objective function instead of $I_o$, which makes the result of MAC more reasonable. 
According to the results shown in Tab. \ref{tab:find_mac}, $I_o$ and $\bm{I}_b$ are affected by the equivalent resistance $R_o$ of external electrical appliance, the battery's electromotive force $u_b$, and internal resistance $r_b$. 
This means that if $I_o$ is used as the objective function, even for the same RBS structure, the MAC result and corresponding switch state could be changed due to different external electrical appliances. 
This increases the difficulty and uncertainty in RBS structure design. 
On the contrary, by using $\eta$ as the objective function, which dividing $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results is eliminated, as shown in Tabs. \ref{tab:given_x} and \ref{tab:find_mac}.
$\eta$ only reflects the maximum output current capability of the RBS structure.
Assuming that the maximum allowed current of battery cells in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by calculating the $\eta$ of the structure. 
Therefore, compared to $I_o$, $\eta$ is more suitable for structure design. 
Most of the currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} have simple topological characteristics, and the calculation of MACs are relatively simple, even intuitive.
However, when complex and flexible structures need to be designed for application scenarios such as equalization or isolation of specific battery cells, the estimation of MAC will become complex and complicated. 
The method proposed in this paper can effectively solve any RBS structure and estimate MAC universally, paving the way for the structure design of more complex and flexible RBSs.

@@

% \section{Appendix}
% \begin{algorithm}
%     \caption{Get the max available currents of a certain RBS}\label{alg:eta_RBS}
%     \KwData{Directed graph model $G(V,E)$ of the RBS}
%     \KwResult{$\max \eta$}
%     \For{$i \in E_b$}{
%         $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
%         $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
%     }
%     get $\bm{A}$ by Equation \ref{eq:A}\;
%     \While{not yet determine $\max \eta$ }
%     {
%         $N_{sel} \leftarrow \text{number of selected $SP$s calculated by dichotomy}$\;
%         $C_b    \leftarrow \text{set of all combinations of $N_{sel} $~batteries from $N_b$}$\;
%         \For{$c_b \in C_b$}{
%             $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
%             $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
%             get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
%             \eIf{$\bm{Y}_n$ is invertible}{
%             }{construct an effective solution}
%             get $I_o$ by Equation \ref{eq:I_o}\;
%             get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
%             \eIf{$\max(\bm{I}_b)\leq I_m$}{
%                 $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
%             }{break}
%         }
%     }
% \end{algorithm}

\bibliographystyle{ieeetr}
\bibliography{my_ref}
